The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-01-30 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

It's worth noting that much of this paper discussed the the effects from an
offensive point of view, focusing on a teams ability to score. However, one 
of the main factors that influence an offense's ability to score is the opposing
defense. It's possible that home court advantage mainly functions as an extra defender
for home teams, which is how it negatively impacts away scoring. There is not much
home fans can do to help their team on offense, except being quiet so players can 
easily communicate and focus. However, when on defense fans can support their team
by cheering loudly and making it harder on the offense. This would explain how away 
teams were able to improve offensively in the bubble. Home teams did not have the 
regular help from the noise of fans that hinder the away team's offensive efforts. 
This would also explain why home team offense didn't show significant change in the 
bubble, the in-game offensive environment was largely unaltered for home teams
since the bubble provided the same quiet environment they're used to at home while
on offense. Meanwhile, removing the "sixth defender" from home team defensive efforts 
allowed away teams to work more effectively on offense.

>>>>

It's worth noting that much of this paper discussed the the effects from an
offensive point of view, focusing on a teams ability to score. However, one
of the main factors that influence an offense's ability to score is the opposing
defense. It's possible that home court advantage mainly functions as an extra
defender for home teams, which is how it negatively impacts away scoring. There
is not much home fans can do to help their team on offense, except being quiet
so players can easily communicate and focus. However, when on defense, fans can
act as a "sixth defender" supporting their team by cheering loudly and making it
harder on the offense. This would explain how away teams were able to improve
offensively in the bubble. Home teams did not have the regular help from the
noise of fans that hinder the away team's offensive efforts. This would also
explain why home team offense didn't show significant change in the bubble, the
in-game offensive environment was largely unaltered for home teams since the
bubble provided the same quiet environment they're used to at home while on
offense. I still believe home court advantage is better categorized as a
negative effect on away team offense, since it's more likely
noise from fans lowers level of play of away offense rather than raise the level
of play of home defense. This will be further discussed below.
